---
title: "WHO CES Analysis"
output: 
  rmarkdown::html_vignette:
    keep_md: true
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{WHO CES Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("images/SCI_Foundation_RGB_Navy_Long_red.jpg"),  
               alt = 'logo', 
               style = 'position: absolute; top: 0; right: 0; margin-right: 75px; padding:1px; border:1px; width: 322px; height: 65px')
```

```{r, include = FALSE}
options(width = 120)
```

<br>
This vignette details how to perform the standard analysis calculations for a coverage survey which has followed the [WHO Coverage Survey Evaluation Methodology](https://apps.who.int/iris/bitstream/handle/10665/329376/9789241516464-eng.pdf).

<br>

# Loading data, libraries and first look at the data

Before starting we need to call the necessary `R` libraries as well as the underlying data. The `sciCoverageR` package contains a data frame called `vignette_ind` exemplifying data from a WHO Coverage Evaluation Survey methodology survey.  It contains 7049 rows, representing the individuals interviewed and 117 columns.

```{r, results='hide', message = FALSE}
# Load libraries
library(sciCoverageR)
library(dplyr)
library(survey)
library(purrr)
```

```{r, warning = FALSE}
# Load data, examine dimensions, look at 
data(example_ind, package = "sciCoverageR")
dim(example_ind)
```

What the variables contain and how they are coded is recorded in the SCIF data dictionary for a CES. See the data dictionary for more details about the variables. In this example survey, only SAC were interviewed (the only response to `ind_group` is `"1_SAC"`).

```{r}
# Example of variable names contained in the example data file
head(names(example_ind))

# Check the answer codes to ind_group
unique(example_ind$ind_group)
```

<br>

# Setting up survey design

The example data comes from a survey of four implementation units (IUs), with 30 subunits selected per IU using the [Coverage Survey Builder]( https://www.ntdsupport.org/sites/default/files/uploads/docs/resources/Coverage%20Survey%20Builder_v2.11.xls). In this example dataset the IU is the health district, captured by the `moh_1` variables. The second stage of sampling is selecting the households in the segment, while the third stage is selecting the individuals. In the case of the CES methodology all individuals in a chosen household ought to be selected.

In order to analyse the survey data, the survey design needs to be inputted. This is done using the `svydesign` function of the previously loaded `survey` package. The `svydesign` function allows for setting of a finite population correction (fpc) factor at each sampling stage. This is not done here for simplicity. Generally speaking, the design of the survey may vary and thus setting the design is not automatised but rather should be thought about by the analyst assigned to the survey and then set up manually.  

A discussion about the use of different survey designs is beyond the scope of this vignette. It should be just noted that on page 27, [the WHO CES guidance](https://apps.who.int/iris/bitstream/handle/10665/329376/9789241516464-eng.pdf) claims that:

> _Because the survey methodology employed produces an equal probability sample,  sample  estimates  can  be  calculated  without  the  use  of  sample  weights._

```{r}
# Requires survey design
cs_design <- svydesign(ids = ~ segment_name + hh_house_code + ind_code,
                       data = example_ind)
cs_design
```

<br>

# Using the `estimate_cs_values` function 

## Standard use

Once the design is set, the survey coverage and reach can be calculated using the package’s own `estimate_cs_values` function. The function takes three arguments: 

1. `var` codes the binary variable of interest: e.g., answers to whether the individual was offered Praziquantel (`ind_offered_pzq_bin`) or whether the individual swallowed Albendazole (`ind_swallowed_alb_bin`).

2. `part` codes by which variable the data should be partitioned. This should commonly be the IU.

3. `design` is the `survey` design object created by the user for this survey.

The output will give values per partition for the overall value, the value broken down by sex and - if the respondents are SAC - broken down by school attendance.

Using the just created `cs_design` object, partitioning by the Health District (`moh_1_label`) to obtain the estimate of the survey reach for PZQ we just need to input the relevant variables into the function:

```{r}
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = cs_design)
```

The output follows the [_tidy data_ format](https://r4ds.had.co.nz/tidy-data.html), so it can be subsequently used as a data frame for the production of data visualisation. The output is a data frame containing 9 columns. The columns are:

1. `partition` - The unique values contained in the `part` variable passed on to the function

2. `group` - The group (SAC or adults) the estimates refer to. If both SAC and adults are contained, the function will append the adult results to the SAC results into a single data frame.

3. `drug` - The drug the variable passed to the function as the `var` argument refers to.

4. `by` - The characteristics by which the information is broken down by (per partition). There are three distinct characteristics: `overall` is the overall result, i.e., not broken down; `sex`, by the sex of the individuals; `attendance`, by the fact whether the individual does or not attend school. The latter only applies to SAC.

5. `sex` - Is `NA` for all values bar those broken down by `sex`, when it denotes what sex the results refer to.

6. `attendance` - Is `NA` for all values bar those broken down by `attendance`, when it denotes whether the child attends school (value `1` for yes) or not (value `0` for no).

7. `estimate` - The point estimate for the survey reach or coverage

8. `lower` - The lower limit of the confidence interval (at the desired confidence level, by default this is 95%) for the estimate for the survey reach or coverage.

9. `upper` - The lower limit of the confidence interval for the estimate for the survey reach or coverage.

In certain cases, the MDA targeted different drugs in different areas. In the case of this example data, for instance, PZQ was distributed in all health districts, but ALB only in two. This can be seen by looking at the number of non-missing answers to the `ind_offered_pzq_bin` and `ind_offered_alb_bin` variables per health district.

```{r}
table(example_ind$moh_1_label, is.na(example_ind$ind_offered_pzq_bin))
table(example_ind$moh_1_label, is.na(example_ind$ind_offered_alb_bin))
```

The function will only return the results for partitions (here IUs) where at least one non missing answer is given. Since in health districts `B` and `C` all answers for ALB are missing, the results for these IUs are not computed. The output has 10 instead of 20 rows.

```{r}
estimate_cs_values(var = "ind_offered_alb_bin", part = "moh_1_label", design = cs_design)
```

## The partition argument

The partition argument (shortened to `part`) argument will divide the data by the unique units present in the variable passed to the argument. It is intended for the implementation unit, but any other variable could be used. If we wanted, for example, to have the overall results of the survey we can pass to partition an argument that is the same for all individuals, like the country code.

```{r}
estimate_cs_values(var = "ind_offered_pzq_bin", part = "country_code", design = cs_design)
```

Note however, that the survey was not designed to give a country level summary and thus, though the value can be computed, it is not a nationally representative estimate of country wide survey reach.

Another option is to use the equity tool quintiles, to obtain the values per quintile.

```{r}
estimate_cs_values(var = "ind_offered_pzq_bin", part = "hh_national_equity_quintile", 
                   design = cs_design)
```

## Using additional arguments

The function has two additional arguments that have default values. The argument `level` defines the confidence level at which the confidence interval is calculated. It is set per default at 0.95 but can be set any level we may need. We can compare the first row of the output for the survey reach for PZQ with the default setting and manually setting it at 95%.

```{r}
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = cs_design)[1,]
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = cs_design, 
                   level = 0.95)[1,]
```

We can see the results are the same In comparison, at 90% the interval narrows, while at 99% it widens.

```{r}
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = cs_design, 
                   level = 0.9)[1,]
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = cs_design, 
                   level = 0.99)[1,]
```

Finally, we can also set the degrees of freedom, which also impact the interval estimation. By default, the estimation takes the degrees of freedom from the `design` object. This is the recommended method. However, for certain estimates, there are not enough degrees of freedom to calculate the interval. 

The survey package function calculates the degrees of freedom as one less than the number of first level units, that is the number of unique units contained in the first variable passed to the `ids` argument of `svydesign`. In our case, we inputted `segment_name`, which has 120 distinct entries, 30 for each IU. The degrees of freedom are thus:

```{r}
degf(cs_design)
degf(subset(cs_design, moh_1_label == "Health District A"))
degf(subset(cs_design, segment_name == "segment_1"))
```


Hence the estimate for each health district is calculated with 29 degrees of freedom. We can see that leaving the default or manually passing this argument leads to the same result.

```{r}
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = cs_design)[1,]
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = cs_design, 
                   degf = 29)[1,]
```

For cases where the degrees of freedom are 1 or less, the method to calculate the confidence interval fails, and we may need to enter the degrees of freedom manually to estimate the confidence interval. This is for example the case if we wanted to obtain segment level estimates (for which the degrees of freedom are 0). In the example data set this would not be possible due to an error, yet how to nonetheless obtain these estimates is covered in the error flagging section. Before we look how to  leverage the `map` function from the `purrr` package to obtain a single data set with all estimates.

## Using function - Purrrfect

The `map` function allows us to directly pass a list of arguments as the first argument of any function. This means, here, that we can create a list with all the variables we are interested in. The logic of the `map` function is not further discussed here, but further reading is [available here from the R for Data Science book](https://r4ds.had.co.nz/iteration.html#the-map-functions).

For ease of viewing, we will use `country_code` as partition argument, to reduce the number of rows of the output and round the estimates.

```{r, error=FALSE, warning=FALSE}
# Using the fact that the first element is var
vars <- list(reach_pzq = "ind_offered_pzq_bin", 
             coverage_pzq = "ind_swallowed_pzq_bin",
             reach_alb = "ind_offered_alb_bin", 
             coverage_alb = "ind_swallowed_alb_bin")
out <- map_dfr(vars, estimate_cs_values, part = "country_code", design = cs_design, 
               .id = "question")
out %>% dplyr::mutate(dplyr::across(is.numeric, round, 2))
```

<br>

# Data validation

## Evaluate function arguments

The first thing the function we will do is to check whether the three necessary arguments (`level` and `degf` have default values and are not checked) are of the expected format. `var` and `part` need to be a single string. If not, the function will error. Same if the variable passed is not contained in the design objects (not the spelling error in the second case, causing the error.)

```{r, error=TRUE}
estimate_cs_values(var = "ind_offered_pzq_bin", part = 2, design = cs_design)
estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_lable", design = cs_design)
```

Additionally, the design object needs to be a design object created using the `svydesign` function, otherwise, an error will inform us that we have not passed an argument of the expected form.

```{r, error=TRUE}
class(cs_design)
wrong_design <- unlist(cs_design)
class(wrong_design)

estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = wrong_design)
```

Finally, the function will evaluate the variable name is of the standard naming form. The variables coding information on survey reach or coverage are made up of four blocks, connected by an underscore. The first is `ind`, to denote the information is collected at individual level. The second is `offered` or `swallowed` to denote reach and coverage. This is followed by a three letter coding of the drug (e.g., `pzq` or `alb`), and finally `bin` to denote the variable is a binary yes / no question with codes `0` for no and `1` for yes. Hence, using the non-binary question on PZQ reach (allowing for `does not know` as an answer) will give an error and inform us of what the expected argument looks like:

```{r, error=TRUE}
estimate_cs_values(var = "ind_offered_pzq", part = "moh_1_label", design = cs_design)
```

## Evaluate underlying data

The function will also investigate the data contained in the design, not just the arguments in the function. Based on the data dictionary, the function expects:

1. `ind_group` to be present in the data and coded as `1_SAC` or `2_Adult`,

2. `ind_sex` to be present in the data and coded as `1_Male` or `2_Female`, and

3. `ind_child_attend_bin` to be present in the data (if the survey contains SAC) and coded as `0` or `1`.

If the data does not follow these data dictionary conventions, the function will error and inform the user. For example, if we create an alternative data frame and change the coding of `ind_sex` to `m` for male and `f` for female the function will not work:

```{r, error=TRUE, warning=FALSE}
alt_df <- example_ind
alt_df$ind_sex <- ifelse(alt_df$ind_sex == "1_Male", "m", "f")

alt_design <- svydesign(ids = ~ segment_name + hh_house_code + ind_code,
                       data = alt_df)

estimate_cs_values(var = "ind_offered_pzq_bin", part = "moh_1_label", design = alt_design)
```

# Commonly ocurring issues

The second part of the error flagging section focuses on issues that can commonly arise in the data. These may give a warning or an error, which may startle us, but are still a normal reaction of the function to an anormal circumstance. We look at two errors that occur when group information is unique, i.e., there is no variability in the answers.

## Convergence error if responses are unique

The first thing to note is that the output will generate a warning denoting the algorithm has not converged if a group answer to the reach or coverage question is unique (i.e., all `0` or all `1`). Let us reduce the data to only Health District D and amend the answers so all replies made by girls to `ind_offered_alb` are positive and run the `estimate_cs_values` function on this alternative data.

```{r, warning=FALSE}
alt_df <- example_ind %>% filter(moh_1_name == "health_district_d")
alt_df$ind_offered_alb_bin[alt_df$ind_sex == "2_Female"] <- 1

alt_design <- svydesign(ids = ~ segment_name + hh_house_code + ind_code,
                       data = alt_df)
```

```{r}
estimate_cs_values(var = "ind_offered_alb_bin", part = "moh_1_label", design = alt_design)
```

Note the warning message stating the algorithm did not converge. This warning should generally be investigated but we know that it comes from the fact, in this case, that the answers are all positive. The lower and upper confidence interval estimates are also 1 for the reach for girls.

## Answers missing from groups used to break down the data

As mentioned earlier, the degrees of freedom at the segment level are 0, so we can, to estimate the confidence interval, manually set the degrees of freedom to 2. The function fails nonetheless to produce estimates at the segment level.

```{r, error=TRUE, warning=FALSE}
estimate_cs_values(var = "ind_offered_pzq_bin", part = "segment_label", design = cs_design, 
                   degf = 2)
```

The error notice comes form the underlying `svyciprop` function. How such an error has come about may vary and a precise analysis is warranted. One possible solution is that some group variable used to break down the data is not present in the estimation variable data. Since this is a strange phenomenon, we should look in detail at Segment 84, the culprit in this case.

```{r}
example_ind %>% filter(segment_name == "segment_84") %>% 
  summarise(
    HHs = n_distinct(hh_house_code),
    Individuals = sum(!is.na(ind_sex), na.rm = T),
    Girls = sum(ind_sex == "2_Female", na.rm = T),
    `Girls answered` = sum(ind_sex == "2_Female" & !is.na(ind_offered_pzq_bin), na.rm = T),
    Boys = sum(ind_sex == "1_Male", na.rm = T),
    `Boys answered` = sum(ind_sex == "1_Male" & !is.na(ind_offered_pzq_bin), na.rm = T))
```

As we can see from the table output, the data for this segment comes from 12 HHs, only four if which allowed us to interview. If the 5 SAC in these HHs, only 1 could be interviewed. Hence, the subunit has two distinct answers to the `ind_sex` question, but only answers to the `ind_offeref_pzq_bin` variable from one of the sexes. The `svyciprop` function tries to calculate the answer for both and fails to do so, resulting in this error. 

Since in this case, we know the error comes from Segment 84 we can see that dropping the segment to obtain the results for all other ones.

```{r, warning=FALSE}
head(estimate_cs_values(var = "ind_offered_pzq_bin", part = "segment_label", 
                   design = subset(cs_design, !segment_name == "segment_84"), degf = 2))
```
